Studying measurement invariance in factor analysis models via stochastic processes

### 2011-02-10 MIpaper/par_instable.tex
added computational details section, including additional references
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@40 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

>>>>

\section*{Computational Details}

All results were obtained using the {R}~system for statistical computing \cite{R2010},
version~2.11.1, employing the add-on packages {OpenMx}~0.9.1-1421 \cite{BokNea11} for
fitting of the factor analysis models and {strucchange}~1.4.2 \cite{ZeiLei02,Zei06}
for evaluating the parameter instability tests. {R} and {strucchange} are
freely available under the General Public License~2 from the
Comprehensive \proglang{R} Archive Network at \url{http://CRAN.R-project.org/}
while {OpenMx} is available under the
Apache License~2.0 from \url{http://openmx.psyc.virginia.edu/}.
R code for replication of our results is
available at \url{http://semtools.R-Forge.R-project.org/}.
